---
title: "CHOP R 101: Intro to R for Clinical Data"
description: A gentle introduction to data science for healthcare professionals and clinical researchers.
author:
  - name: Stephan Kadauke
    url: https://www.linkedin.com/in/skadauke/
    affiliation: Children's Hospital of Philadelphia
    affiliation_url: https://www.chop.edu
site: distill::distill_website
output_dir: docs
---

<!-- Update site with rmarkdown::render_site("site/") -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Welcome!

This is the website for the short course *Introduction to R for Clinical Data* organized by the CHOP R User Group.

You'll learn about [R Markdown](https://rmarkdown.rstudio.com/), a framework for reproducible data science, and how to perform essential data science tasks such as data import, visualization, transformation, and communication.

For the best experience during the workshop, I suggest the following (none of the below are absolutely necessary!):

- If available to you, use **two monitors** (or another two-screen setup such as a laptop and a tablet or two laptops). 
- To avoid issues caused by the overzealous CHOP firewall, you may want to connect from a personal (not work-issued) device using a non-work wireless network (i.e. `chopguest`). If you are joining from your home network, you should be OK!
- Please use a recent version of macOS or Windows.
- We highly recommend you use the [Google Chrome](https://www.google.com/chrome/) browser to access the RStudio Server training environment. 

The entire course will be recorded and made available to CHOP R User Group members for replay. To protect the privacy of participants, no breakouts, video feeds, or chats will be recorded. We also request that you refrain from recording or screen-grabbing any part of the course. 

## Pre-work

### Essential

- We will be utilizing Zoom for this workshop, please download and install the latest version [here](https://zoom.us/download).
- Install the latest version of [Google Chrome](https://www.google.com/chrome/). 
- We want to provide a welcoming and supportive learning environment for everyone. To help us do so, please take a look at our [code of conduct](conduct.html). 

### Optional (but highly recommended)

- We will have a pre-course technology check session where you will be able to test your connection to Zoom and logging into the RStudio Server training environment. If possible, please plan to attend!
- To help us better understand our learners, please complete the [pre-course survey](https://docs.google.com/forms/d/e/1FAIpQLSflqcTHed2o6VhuAFwlxUXHnN8ulIIjGxYbGm3dlZuHYsXZxQ/viewform). We appreciate it!
- Install [R](https://cloud.r-project.org/) and [RStudio Desktop](https://rstudio.com/products/rstudio/download/) on your computer. We made video with step by step instructions for installing these on macOS ([here](https://www.youtube.com/watch?v=GM88tYlEy_g)) or Windows ([here](https://www.youtube.com/watch?v=JRKmZK5-6aE)).
- You may wish to download and/or print a copy of the course slides. PowerPoint slide decks are available [here](https://github.com/skadauke/intro-to-r-for-clinicians-chop/tree/master/slides). 

## After the course

If you would like to practice with the materials from the course, go to the [GitHub repository](https://github.com/skadauke/intro-to-r-for-clinicians-chop), and click the green button labeled "Code" to download the repository as a .ZIP file. 

To install all the packages we used in the training environment, open RStudio and run the following command in the Console: 

```{r, eval = FALSE, echo = TRUE}
install.packages(c(
  "tidyverse",
  "rmarkdown",
  "shiny",
  "flexdashboard",
  "plotly",
  "DT"
))
```

## Resources

- [R for Data Science](https://r4ds.had.co.nz/) (by Hadley Wickham and Garrett Grolemund)
  - [Solutions Manual](https://jrnold.github.io/r4ds-exercise-solutions/) (by Jeffrey Arnold)
- [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/) (by Yihui Xie, JJ Allaire, and Garrett Grolemund)
- [Fundamentals of Data Visualization](https://clauswilke.com/dataviz/) (by Claus Wilke)
- [RStudio Cheatsheets](https://rstudio.com/resources/cheatsheets/)

## Acknowledgments {.appendix}

This course draws from various sources, most notably Garrett Grolemund's [Welcome to the Tidyverse](https://github.com/rstudio-education/welcome-to-the-tidyverse) and Greg Wilson's [Teaching Tech Together](http://teachtogether.tech/en/). The section of the course discussing dashboards was initially developed by Patrick Mathias. Other sections were improved upon by Amrom Obstfeld and Joe Rudolf. This site uses the [distill](https://rstudio.github.io/distill/) package.