---
title: "CHOP R 101: Intro to R for Clinical Data"
description: A gentle introduction to data science for healthcare professionals and clinical researchers.
author:
  - name: Arcus Data Education
    url: https://education.arcus.chop.edu/
    affiliation: Children's Hospital of Philadelphia
    affiliation_url: https://www.chop.edu
site: distill::distill_website
output_dir: docs
---

<!-- Update site with rmarkdown::render_site("site/") -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Welcome!

This is the website for the short course *Introduction to R for Clinical Data* organized by the CHOP R User Group.

You'll learn about [R Markdown](https://rmarkdown.rstudio.com/), a framework for reproducible data science, and how to perform essential data science tasks such as data import, visualization, transformation, and communication.

For the best experience during the workshop, we suggest the following (none of the below are absolutely necessary!):

- If available to you, use **two monitors** (or another two-screen setup such as a laptop and a tablet or two laptops).
- To avoid issues caused by the CHOP firewall, you may want to connect from a personal (not work-issued) device using a non-work wireless network (i.e. `chopguest`). If you are joining from your home network, you should be OK!
- Please use a recent version of macOS or Windows.
- We highly recommend you use the [Google Chrome](https://www.google.com/chrome/) browser to access the RStudio Server training environment.

The entire course will be recorded and made available to CHOP R User Group members for replay. To protect the privacy of participants, no breakouts, video feeds, or chats will be recorded. We also request that you refrain from recording or screen-grabbing any part of the course.

## Pre-work

### Essential

- We will be utilizing Zoom for this workshop, please download and install the latest version [here](https://zoom.us/download).
- Install the latest version of [Google Chrome](https://www.google.com/chrome/).
- We want to provide a welcoming and supportive learning environment for everyone. To help us do so, please take a look at our [code of conduct](conduct.html).

### Optional (but highly recommended)

- We will have a pre-course technology check session where you will be able to test your connection to Zoom and logging into the RStudio Server training environment. If possible, please plan to attend!
- To help us better understand our learners, please complete the [pre-course survey](https://redcap.link/pre_r_for_clinical_data). We appreciate it!
- You may wish to download and/or print a copy of the course slides. These can be found at <https://joy-payton-chop.quarto.pub/intro-r-workshop/>.
- Install [R](https://cloud.r-project.org/) and [RStudio Desktop](https://rstudio.com/products/rstudio/download/) on your computer. We made video with step by step instructions for installing these on macOS ([here](https://www.youtube.com/watch?v=GM88tYlEy_g)) or Windows ([here](https://www.youtube.com/watch?v=JRKmZK5-6aE)).


## After the course

### Watch a replay!

If you'd like a refresher, we suggest that you download the course materials to your computer and follow along with a [replay of the workshop](https://www.youtube.com/watch?v=XCofS3gZ94o).

Make sure you have both R and RStudio installed (see above).

To download the materials from the course, go to the [GitHub repository](https://github.com/arcus/intro-to-r-for-clinicians-chop), and click the green button labeled "Code" to download the repository as a .ZIP file. Unzip that file. Inside of the folder that was created by unzipping the file, double click `intro-to-r-for-clinicians.Rproj` to open a new RStudio session. You should be able to see the `exercises` folder (among other things) in the **Files** pane.

Now install all the packages we used in the training environment. To do so, run the following command in the **Console**:

```{r, eval = FALSE, echo = TRUE}
install.packages(c(
  "tidyverse",
  "rmarkdown"
))
```

### Join the CHOP R User Group!

If you haven't already done so, please consider joining the CHOP R User Group, which is open to anyone with a CHOP or Penn email address. [Click here to sign up](http://bit.ly/chopRusers)!

We won't spam you, we promise, but you'll get invites to user group meetings (semi-regular, about once a month or so) about all sorts of R-related topics, plus an invite to the Slack channel, where you can chat with folks (and ask questions) about R.

## Resources

- [R for Data Science](https://r4ds.had.co.nz/) (by Hadley Wickham and Garrett Grolemund)
  - [Solutions Manual](https://jrnold.github.io/r4ds-exercise-solutions/) (by Jeffrey Arnold)
- [RStudio Primers](https://rstudio.cloud/learn/primers)
- [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/) (by Yihui Xie, JJ Allaire, and Garrett Grolemund)
- [Fundamentals of Data Visualization](https://clauswilke.com/dataviz/) (by Claus Wilke)
- [RStudio Cheatsheets](https://rstudio.com/resources/cheatsheets/)
  - [Data Import Cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/data-import.pdf)
  - [Data Transformation Cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/data-transformation.pdf)
  - [Data Visualization Cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/data-visualization-2.1.pdf)

## Acknowledgments {.appendix}

This course is based closely on material developed by [Stephan Kadauke](https://www.linkedin.com/in/skadauke/). You can see the materials for Stephan's original course, including recordings of the entire workshop, at his course website: [https://skadauke.github.io/intro-to-r-for-clinicians-chop/](https://skadauke.github.io/intro-to-r-for-clinicians-chop/). Thank you, Stephan, for developing such amazing materials and for sharing them under a [Creative Commons license](https://github.com/skadauke/intro-to-r-for-clinicians-chop/blob/master/LICENSE.txt)!

This site is built using the [distill](https://rstudio.github.io/distill/) package.

<!-- Update site with rmarkdown::render_site("site/") -->
