---
title: "Common Errors encountered by Beginner R Programmers"
output: html_document
---

## Sometimes your error is just a warning!

```{r}
library(tidyverse)
```


## The big three errors

```{r}
summary(covid_testing)
```

Error! object 'x' not found: "You never told me about that object! Did you misspell it? Or forget to define it? Hint: check the Environment pane!"



```{r}
covid_testing <- read_excel("Covid_testing.xls")
```

Error! could not find function 'y': "I don't know this function. Maybe you forgot to load a package with library()?"



```{r}
library(readxl)
covid_testing <- read_excel("covid.testing.xls")
```

Error! path does not exist: 'z': "I don't see this file. Maybe it's not in the right place, or maybe you misspelled it? Hint: check the Files pane!"



## Can you predict the error?

Read the following code and predict the error!

```{r}
library(readxl)
covid_testing <- read_excel("covid_testing.xls")
summary(Covid_testing)
```


Read the following code and predict the error!

```{r}
library(readxl)
covid_testing <- read_excel("covid.testing.xls")
summary(covid_testing)
```



## Can you spot the bug in the code? 

Fix the bug in the following code!

```{r}
library(readxl)
covid_testing <- read_excel("covid_testing.xls")
summary("covid_testing")
```



Can you fix all bugs in the following code?

```{r}
library(readxl)
covid_testing <- read_excel("covid_testing.xls")

covid_testing %>%
  select(mrn, first_name, last_name, result, pan_day) %>%
  rename(pandemic_day = pan_day)
  mutate(age_in_days == age * 365
         age_in_seconds == age_in_days * 1440) %>%
  
```


## Unexpected results when you edit R Markdown

Why is there no green triangle for the following code chunk?

``{r} 
plot(mtcars)
```


Missing backticks can have weird side effects! 

```{r}
plot(pressure)
```
